The Migration of the Field Code

### 2016-02-17 index.Rmd
Link to slides
Add working group to the index
Updated slides for DH working group

>>>>

You may also be interested in the materials for various talks we have given about this project.

- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)

### 2016-02-17 talks/dh-working-group-slides/dh-working-group-slides.Rmd
Updated slides for DH working group

---
title: "Tracking the Migration of the Field Code"
author: "Lincoln Mullen and Kellen Funk"
date: "http://lincolnmullen.com"
output: 
  revealjs::revealjs_presentation:
    theme: white
    css: talks.css
    transition: slide
    fig_width: 9
    fig_height: 6
    fig_caption: true
    pandoc_args: [
      "--slide-level=2",
      "--metadata=history:true",
      "--metadata=margin:0.05",
      "--metadata=center:false",
      "--variable=width:1200",
      "--variable=height:700"
    ]
    mathjax: null
    self_contained: true
    center: false
---

@@

@@

@@

## {data-background="code-to-code.png"}

## {data-background="state-to-state.png"}

>>>>

---
title: "The Migration of the Field Code"
author: "Lincoln Mullen and Kellen Funk"
date: "http://lincolnmullen.com"
output: 
  revealjs::revealjs_presentation:
    theme: white
    css: talks.css
    transition: slide
    fig_width: 9
    fig_height: 6
    fig_caption: true
    pandoc_args: [
      "--slide-level=2",
      "--metadata=history:true",
      "--metadata=margin:0.05",
      "--metadata=center:false",
      "--variable=width:1200",
      "--variable=height:700"
    ]
    mathjax: null
    self_contained: true
    center: false
---

@@

## {data-background="code-to-code2.png"}

## {data-background="state-to-state2.png"}

@@

## {data-background="CA1851.png"}

@@

## {data-background="NY1879.png"}
